%!TEX root = ../Final_Assignment_SP_ML4IM_2023.tex
\chapter{Contributions by group members}
\label{ch:contributions}

% für jedes Gruppenmitglied einen eigenen Paragraphen, der die Aufgaben, Anteile an der Ausarbeitung, etc. beschreibt
% zusammengenommen eine halbe bis ganze Seite

\section{Maximilian Elfers}

The main task was the creation of the preprocessing code and workflow of the raw videos. During the course of the semester another big task was the continous training of models on PALMA, which turned out to be more difficult than hoped, because of technical problem on PALMA with YOLO. \\
In the written assignment the contribution was the related work and discussion chapter and shared tasks for the methods and results chapter.

\section{Timo Lietmeyer}
The preprocessing code and the conversion of bounding boxes have been extended. In addition, minor bugs in the code and during execution were fixed and problems with the use of YOLO on PALMA were solved. \\
In the written assignment, the Fundamentals part was added and the Methods, Results and Methods part was created in cooperation.

\section{Hendrik Lüning}
A major part of the work was the conversion of the bounding boxes described in \ref{ch:methods}, which involved setting up the build-dataset script and adapting it to the RGB data. As there were many problems with this script, a lot of debugging was done. Once the build-dataset script was complete, the focus shifted to training the models.\\
In the final draft, the introduction and, in collaboration, the methods-, results- and discussion-section were added.
